Canonical rings of $\bq$-divisors on Minimal Rational Surfaces

### 2015-07-31 surfaces-write-up/surface-write-up.tex
responses to todos

Aaron: What does plural mean here?
I was thinking of doing something along the lines of
$R$ is generated in degree at most $g$ with relations in degree at most $r$.}

@@

Aaron: How does $E_\mu$ depend on $i$? If you'd prefer to just say everything depends on $i$, I'm ok with it, though I still think including $i$ subscripts would be slightly
preferable. Perhaps just say near the beginning a list of all the things that will depend on $i$. I don't think you can say "everything for the remainder of the proof depends on i", because that's not true, e.g., $\ell_j$ for $j \neq i$ doesn't depend on $i$, though of course this is very confusing because you write $\ell_i$ in the definition of $\deg E$. (Won't this be more difficult than just writing a supscript or superscript $i$ though?)
}
we simply write $f_i$ as a 
polynomial in $f_1, \ldots f_4$. Furthermore, these
generate all relations, since they allow us to reduce any $\prod_{j =
1}^n f_j^{c_j}$ to the canonical form where $r_i = - \lfloor d \alpha_i
\rfloor$ whenever $i > 4$.  To bound the degree of generation of these relations, we bound the degree of generation of the ideal $(z_i - \beta_i) \cap \ker(\psi)$ for each $i$.

@@

\todo{Aaron:
Does $E$ depend on $\omega$? I.e. have we fixed an $\omega$ for the rest of the proof?
If so, why can we do this?
}
\todo{Aaron: If $i$ has been fixed for the remainder of the proof, why 
are we using $i$ as dummy subscripts everywhere?}
with $E$ of the form
\begin{equation}\label{eqn:hirz-E-translation}
	E = \begin{cases}
	\frac{1}{\kappa_i} e_i  	&  \mbox{ if }i\in \Te\\
	\sum_{j\in \Tm} r_{i,j} e_{i,j}: r_{i,j}\in \bq, \sum_{j\in \Tm} r_{i,j}\kappa_{i,j}' = 1 & \mbox{ if } i\in \Tp\\
	\sum_{j\in \Tp} r_{j,i} e_{j,i}: r_{j,i} \in \bq, \sum_{j\in \Tp} r_{j,i} \kappa_{i,j}'' = 1 	& \mbox{ if } i\in \Tm\\
	\end{cases}.
\end{equation}
Specifically, if we write out $\omega = \sum_{j\in \Te} s_j e_j + \sum_{j\in \Tp, k \in \Tp} s_{j,k} e_{j,k}$, then any choice of $r_{j,k}$'s not greater than the respective $s_{j,k}$'s such that $r_{i,j} \kappa_{i,j}' =1$ (when $i\in \Tp$ but a similar statement holds for $i\in \Tm$) will suffice.  Such a choice of $r_{i,j}$'s uniquely determines the necessary $\lambda$.

>>>>

Aaron: What does plural mean here?
I was thinking of doing something along the lines of
$R$ is generated in degree at most $g$ with relations in degree at most $r$. \\
Peter: The plural is signifying it is not just generated in 1 degree.  It is generated in all the degrees up to $g$ with relations generated in degrees all the degrees up to $r$.}

@@

Aaron: How does $E_\mu$ depend on $i$? If you'd prefer to just say everything depends on $i$, I'm ok with it, though I still think including $i$ subscripts would be slightly
preferable. Perhaps just say near the beginning a list of all the things that will depend on $i$. I don't think you can say "everything for the remainder of the proof depends on i", because that's not true, e.g., $\ell_j$ for $j \neq i$ doesn't depend on $i$, though of course this is very confusing because you write $\ell_i$ in the definition of $\deg E$. (Won't this be more difficult than just writing a supscript or superscript $i$ though?)
\\
Peter: Where does $\ell_j$ appear?  It may be a typo... I can't remember...  I think there are only $\ell_i$'s and $\ell_{i,j}$'s.  Anyway, what I meant was every new variable defined after this point depends on $i$, not every variable used.
}
we simply write $f_i$ as a 
polynomial in $f_1, \ldots f_4$. Furthermore, these
generate all relations, since they allow us to reduce any $\prod_{j =
1}^n f_j^{c_j}$ to the canonical form where $r_i = - \lfloor d \alpha_i
\rfloor$ whenever $i > 4$.  To bound the degree of generation of these relations, we bound the degree of generation of the ideal $(z_i - \beta_i) \cap \ker(\psi)$ for each $i$.

@@

\todo{Aaron:
Does $E$ depend on $\omega$? I.e. have we fixed an $\omega$ for the rest of the proof?
If so, why can we do this?
\\
Your write, it depends on $\omega$, not just $i$.  We can do this, because we will take the maximum over all $\omega$.  What I mean by this, is for any starting relation (with initial term $\omega$ under some appropriate order) we reduce it to a different relation of the form described in the proof.  We then take the maximum of the degrees of the relation that any $\omega$ is reduced to.
}
\todo{Aaron: If $i$ has been fixed for the remainder of the proof, why 
are we using $i$ as dummy subscripts everywhere?\\
I don't follow; as in $e_i$'s?  or $e_{i,j}$'s?  $i$ is fixed in all of these statements, whereas $j$ ranges as necessary ($j$ is not fixed).}
with $E$ of the form
\begin{equation}\label{eqn:hirz-E-translation}
	E = \begin{cases}
	\frac{1}{\kappa_i} e_i  	&  \mbox{ if }i\in \Te\\
	\sum_{j\in \Tm} r_{i,j} e_{i,j}: r_{i,j}\in \bq, \sum_{j\in \Tm} r_{i,j}\kappa_{i,j}' = 1 & \mbox{ if } i\in \Tp\\
	\sum_{j\in \Tp} r_{j,i} e_{j,i}: r_{j,i} \in \bq, \sum_{j\in \Tp} r_{j,i} \kappa_{i,j}'' = 1 	& \mbox{ if } i\in \Tm\\
	\end{cases}.
\end{equation}
Specifically, if we write out $\omega = \sum_{j\in \Te} s_j e_j + \sum_{j\in \Tp, k \in \Tp} s_{j,k} e_{j,k}$, then any choice of $r_{j,k}$'s not greater than the respective $s_{j,k}$'s such that $r_{i,j} \kappa_{i,j}' =1$ (when $i\in \Tp$ but a similar statement holds for $i\in \Tm$) will suffice.  Such a choice of $r_{i,j}$'s uniquely determines the necessary $\lambda$.
